---
title: "Assignment 11 (S-520)"
author: "FNU Anirudh"
date: "December 2, 2015"
output: word_document
---

#Solution 1:- 
```{r,eval=TRUE}
# 144 Races
observed<- c(29,19,18,25,17,10,15,11)
# Ho:- Horse's starting position does not affect winning
expected<-rep(144/8, 8)
# LR chi-squared test
G2 = 2 * sum(observed * log(observed/expected))
1 - pchisq(G2, df=7)
# Pearson's chi-squared
X2 = sum((observed - expected)^2 / expected)
1 - pchisq(X2, df=7)
```

We can see that both results yield value less than 0.05 hence we can
reject our Null Hypothesis that horse's starting position does not
affect it's chance of winning. ( I am assuming 95% Confidence
Interval) since it's not mentioned in problem.


#Solution 2:-

```{r, eval=TRUE}
height<- c(3/4,1/4)
leaves<- c(3/4,1/4)
dominant<- c(3/4,3/4)
recessive<- c(1/4,1/4)
# a) Probability of Each Ej
E1<- 3/4*3/4
E1
E2<- 3/4*1/4
E2
E3<- 1/4*3/4
E3
E4<- 1/4*1/4
E4
# b)
observed<- c(926,288,293,104)
observed
# n=1611 given in the problem
expected<-c(E1,E2,E3,E4)*1611
expected
# LR chi-squared test
G2 = 2 * sum(observed * log(observed/expected))
G2
# Degrees of Freedom= 3
1 - pchisq(G2, df=3)
# Pearson's chi-squared
X2 = sum((observed - expected)^2 / expected)
X2
1 - pchisq(X2, df=3)

```
From P-value we cannot reject our Null Hypothesis hence both
observed and expected values are more or less similar which shows
the correctness of cell probabilities calculated.


#Solution 3:- 
```{r,eval=TRUE}
threeft<- c(173,150)
thirtyfive<- c(125,73)
male<- c(173,125)
female<- c(150,73)
observed<- c(173,125,150,73)
N=sum(observed)
e1=(sum(male)*sum(threeft))/N
e2=(sum(male)*sum(thirtyfive))/N
e3=(sum(female)*sum(threeft))/N
e4=(sum(female)*sum(thirtyfive))/N
expected<- c(e1,e2,e3,e4)
expected
observed
# Degree of Freedom= (r-2)(c-1)= 1
# LR chi-squared test
G2 = 2 * sum(observed * log(observed/expected))
G2
1 - pchisq(G2, df=1)
# Pearson's chi-squared
X2 = sum((observed - expected)^2 / expected)
X2
1 - pchisq(X2, df=1)

```
From our p-value, we can conclude that sex ratio of
Panamanian sandflies varies with height above ground and we can reject our null hypothesis of Independence across categories.

#Solution 4:- 
```{r,eval=TRUE}
observed<-c(74,18,12,68,16,12,154,54,58,18,10,44)
N=sum(observed)
LP<-sum(74,18,12)/N
NS<-sum(68,16,12)/N
MC<-sum(154,54,58)/N
LD<-sum(18,10,44)/N
type<- c(LP,NS,MC,LD)
positive<- sum(74,68,154,18)/N
partial<- sum(18,16,54,10)/N
none<- sum(12,12,58,44)/N
response<- c(positive,partial,none)
expected<- (type*response)*N
X2 = sum((observed - round(expected,2))^2/round(expected,2))
# Degrees of Freedom = (r-2)(c-1)= 2*3= 6
1 - pchisq(X2, df=6)

```

P- value is very low which suggests dependence i.e Patient's response to treatment for Hodgkin's disease varies by histological type.

#Solution 5:-

```{r,eval=TRUE}
source('binorm.R')
x<- c(4.813,3.449,2.558,1.657,3.988,3.250,3.568,3.248,2.921,3.116,3.208
      ,4.025,3.302,2.017,3.394,4.482,2.583,3.271,2.107,3.551,2.034,4.189
      ,3.493,3.268,3.985,2.492,3.006,3.613,3.203,3.415,3.804,1.578,3.848
      ,3.211,2.925,2.549,3.598,3.985,1.843,2.651)
y<- c(5.505,3.576,2.316,1.042,4.339,2.988,2.538,2.991,3.453,3.178,3.235
      ,4.391,3.368,1.551,3.498,1.246,3.931,2.959,4.604,2.563,1.575,4.623
      ,3.639,3.320,4.334,4.060,3.333,2.475,3.055,2.756,4.078,0.930,4.140
      ,3.240,2.835,3.980,2.495,1.949,4.978,3.836)
# a)
qqnorm(x)
# From QQ Plot, We can say that X is drawn from population close to Normal Distribution.

# b)
qqnorm(y)
# From QQ Plot, We can say that Y is drawn from population close to Normal Distribution.

# c) Scatter Plot of (x,y)
binorm.scatter(cbind(x, y))
cor(x, y)

```

Since density of data doesn't fit inside ellipse we can say that they are not from bivariate distribution.

#d)
X and Y may be drawn from two different normally distributed population assuming correlation is just by chance.

#Solution 6:-
```{r,eval=TRUE}
count<- c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14)
freq<- c(57,203,383,525,532,408,273,139,45,27,10,4,0,1,1)
# a) Average Observed Count 
x_bar=sum(count*freq)/sum(freq)
x_bar
# b) 
count1<- c(0,1,2,3,4,5,6,7,8,9)
freq1<- c(57,203,383,525,532,408,273,139,45,27)
# Expected Value for 0-9 values
expected1= dpois(count1,x_bar)*2608
expected1
# Expected value for count greater than 10
expected2=(1-ppois(9,x_bar))*2608
expected2
# Combining all the values
expected=c(expected1,expected2)
expected
# Observed Values
observed<- c(57,203,383,525,532,408,273,139,45,27,16)
# LR chi-squared test
G2 = 2 * sum(observed * log(observed/expected))
p=1-pchisq(G2,9)
# Pearson's chi-squared
X2 = sum((observed - expected)^2 / expected)
1 - pchisq(X2, df=9)

```

Unrestricted dimension is 10 where as restricted dimension is 1
hence degree of freedom df=9.
If count of alpha particle scintillations follow a Poisson
distribution then p= 0.12534 for likelihood ratio test statistics.
Hence we cannot dismiss Null Hypothesis that data was drawn from
Poisson istribution.
Also using Pearson's chisquared test we get larger p value which
fails to reject the null hypothesis.
