---
title: "Take Home2 (S-520)"
author: "FNU Anirudh"
date: "November 9, 2015"
output: word_document
---


Solution 1


```{r,eval=TRUE}
salaries = read.table(file.choose(), header=TRUE)
Faculty = salaries$Salary[salaries$Job == "Faculty"]
Athletics = salaries$Salary[salaries$Job == "Athletics"]
boxplot(Faculty,Athletics,main="Box Plot",horizontal = TRUE,
        names=c("Faculty","Athletics"),col=c("blue","green"))

```

Median salary of Faculty is more than median salary of Athletics and there are more outliers in Athletics than Faculty, There is one huge outlier in athletics compared to faculty.


Solution 2


```{r, eval=TRUE}
t.test(Faculty,Athletics)
qqnorm(Faculty,main = "QQ Plot for Faculty")
qqnorm(Athletics,main = "QQ Plot for Athletics")
plot(density(Faculty))
plot(density(Athletics))

```

Welch's Two-Sample t-test is based on assumption that samples are 
normally distributed.We cannot trust p -value because  we can see 
from QQ Plot and density plot that 

* both faculty and athletics are not normally distributed.
* sample size is relatively small
* There are huge outliers in both faculty and athletics (There is
huge outlier in athletics which will effect mean to very large extent)
and welch's t-test involves calculations with mean.


Solution 3


```{r,eval=TRUE}
logfac=log(Faculty)
logath=log(Athletics)
qqnorm(logfac,main="Faculty After Transformation")
qqnorm(logath,main = "Athletics After Transformation")
var1=var(logfac)
var2=var(logath)

```

We should use Welch's two sample test since data is close to normal
distribution after taking log and variances of the samples are not equal. Student's t-test could have been used if variance values were
equal or closer hence Welch's two sample test seems plausible. 


Solution 4


```{r,eval=TRUE}
m1=mean(logfac)
m2=mean(logath)
Delta = mean(logfac) - mean(logath)
se = sqrt(var(logfac)/50 + var(logath)/50)
Tw = Delta/se
nu = (var(logfac)/50+var(logath)/50)^2/((var(logfac)/50)^2/49+(var(logath)/50)^2/49)
Pvalue = 2*(1-pt(abs(Tw),df=nu))
Pvalue
# Welch 95% confidence interval
q = qt(0.975, df=nu)
lower = Delta - q*se
lower
upper = Delta + q*se
upper

```

Since P-value is less than 0.05, we can reject our null hypothesis.


Solution 5



```{r,eval=TRUE}
summary(Faculty)
summary(Athletics)
par(mfrow=c(1,2))
hist(Faculty,prob=TRUE)
lines(density(Faculty),col="blue")
hist(Athletics,prob=TRUE)
lines(density(Athletics),col="red")

```

We can see that Mean and median for Faculty is more than Athletics and
there is huge outlier in Athletics (double of outlier in faculty) as seen in summary. From Histogram we can say that faculty and athletics don't have same distribution.