---
title: "Assignment 12 (S-520)"
author: "FNU Anirudh"
date: "December 10, 2015"
output: word_document
---

#Solution 1

Successfull Flight Maneuver should depend on skill and chance, so for
a particular candidate, performance on next flight maneuver will be less than his previous performance because we can't expect chance factor(random) to be equally good on his next manuever even though skills are same.This can be attributed to Regression to Mean.


#Solution 2

```{r,eval=TRUE}
x<- c(-0.2,-0.9,-0.4,0.6,0.4)
y<- c(0.4,-0.3,-0.3,0.5,1.1)
# a) Pearson's Correlation Coefficient is given by
print("Pearson's Correlation Coefficient is =")
r=cor(x,y)
r
# b)
plot(x,y)
# Predict y from x
slope = r *(sd(y) / sd(x))
intercept = mean(y) - (slope * mean(x))
predictions = intercept + slope*x
SSE = sum((y - predictions)^2)
abline(intercept, slope, col="red")

# Equation of line y=intercept + slope*x
# In this case, Equation is y=0.36 + 0.80x
# c)
# Predict x from y
plot(y,x)
slope2 = r *(sd(x) / sd(y))
intercept2 = mean(x) - (slope * mean(y))
predictions2 = intercept + slope*y
SSE2 = sum((x - predictions)^2)
abline(intercept2, slope2, col="blue")

# Equation of line here is x=intercept1 + slope2* y
# x=-0.32 + 0.84y

# d) Scatter Plot
source('C:/Stats/Assignment 11/binorm.R')
plot(x,y)
abline(intercept, slope, col="red")
abline(intercept2, slope2, col="blue")
binorm.scatter(cbind(x, y))
abline(intercept, slope, col="red")
abline(intercept2, slope2, col="blue")


```

#Solution 3

```{r, eval=TRUE}
sister<- c(69,64,65,63,65,62,65,64,66,59,62)
brother<- c(71,68,66,67,70,71,70,73,72,65,66)
all<- c(sister,brother)
mb=mean(brother)
ms=mean(sister)
mall=mean(all)
n=length(sister)
sx=sum((sister-ms)^2)/(n-1)
sy=sum((brother-mb)^2)/(n-1)
r=cor(sister,brother)
r2=r^2
# a) The sample coefficient of determination, the proportion of
# variables "explained" by simple linear regression is square of 
# correlation coefficent
r2
SST = sy*(n-1)
SSR = r2 *SST
SSE=(1-r2)*SST
df1=1
df2=9
msr=r2*SST
mse=SSE/df2
f=(n-2)*r2/(1-r2)
1-pf(f,df1,df2)
# b) Ho:beta>0 
# Since p-value>0.05, we fail to reject Null Hypothesis hence we
# cannot say that knowing sister's height helps one predict her
# brother's height.
# c)
syy=sqrt(sy)
sxx=sqrt(sx)
beta1=r*(syy/sxx)
gt=qt(0.95,df2)
se=((1-r2)*sy)/((n-2)*sx)
print("Confidence Interval is=")
lower=beta1- (gt*sqrt(se))
upper=beta1+ (gt*sqrt(se))
lower
upper
# d) Given L=0.1



```

#Solution 4



#Solution 5

```{r,eval=TRUE}
ext=read.table('C:/Stats/Assignment 12/examanxiety.txt',header = TRUE)
exam<-ext$Exam
anxiety<-ext$Anxiety
b = cor(exam, anxiety) * sd(exam) / sd(anxiety)
a = mean(exam) - b * mean(anxiety)
plot(anxiety, exam,main="Plot of Exam Vs Anxiety",xlab="Anxiety",ylab="Exam")
abline(a, b, col="red")

# Equation of line is y=a+bx
# Exam=111-0.73* Anxiety

# b)
fit<-lm(Exam~Anxiety,data = ext)
par(mfrow=c(2,2),mar=c(4,4,2,1))
# Plot to check for Homodeskascity, Normality of errors, Independence
# of errors
plot(fit)
# From Plot, we conculde that out of all assumptions only assumption
# about normality of error seems true.

# c)
# Suppose X and Y are bivariate normal.Then given a specific value
# of X, Y follows normal distribution.
# cor(anxiety,exam)=-0.439 correlation is negative hence we should 
# not use bivariate normal and instead fit an ellipse in scatter plot
# ellipse won't fit density but will be cross like shape.

```

#Solution 6

```{r,eval=TRUE}
fit1<-lm(Exam~Anxiety+Revise+Gender,data=ext)
fit2<-lm(Exam~Anxiety+Revise,data=ext)
summary(fit1)
summary(fit2)

```

From above we can say that model should be Exam~ Anxiety+Revise
since exam scores depend on Revision and Anxiety before the exam, Exam score has nothing to do with gender of person.R^2^ value decreases when Gender is included and Residual Standard error increases hence model should be Exam~Anxiety+Revise.