---
title: "Take Home Final (S-520)"
author: "FNU Anirudh"
date: "December 12, 2015"
output: word_document
---

#Solution 1

```{r,eval=TRUE,warning=FALSE}
table60<- read.table('C:/Stats/TAKEHOME FINAL/election1960.txt',header=TRUE)
fit1<- lm(Party~Income,data = table60)
summary(fit1)
plot(table60$Income,table60$Party)
abline(fit1,col="red")
slope = cor(table60$Income,table60$Party) * sd(table60$Party) / sd(table60$Income) 
intercept = mean(table60$Party) - slope * mean(table60$Income)

```

The equation of regression line is y=slope1* x + Intercept1
i.e. Party=0.104* Income + 3.266

#Solution 2

```{r, eval=TRUE,warning=FALSE}
table80<- read.table('C:/Stats/TAKEHOME FINAL/election1980.txt',header=TRUE)
fit2<- lm(Party~Income,data = table80)
summary(fit2)
slope2 = cor(table80$Income,table80$Party) * sd(table80$Party) / sd(table80$Income) 
intercept2 = mean(table80$Party) - slope2 * mean(table80$Income)
plot(table80$Income,table80$Party)
abline(fit2,col="blue")

```

The equation of regression line is y=slope2* x + Intercept2
i.e. Party=0.352* Income + 2.528

#Solution 3
```{r,eval=TRUE,warning=FALSE}
table20<- read.table('C:/Stats/TAKEHOME FINAL/election2000.txt',header=TRUE)
fit3<- lm(Party~Income,data = table20)
summary(fit3)
slope3 = cor(table20$Income,table20$Party) * sd(table20$Party) / sd(table20$Income) 
intercept3 = mean(table20$Party) - slope3 * mean(table20$Income)
plot(table20$Income,table20$Party)
abline(fit3,col="green")

```

The equation of regression line is y=slope3* x + Intercept3

i.e. Party=0.342* Income + 2.657

#Solution 4

```{r,eval=TRUE,warning=FALSE}
table60$Year<-rep("1960",nrow(table60))
table80$Year<-rep("1980",nrow(table80))
table20$Year<-rep("2000",nrow(table20))
table_new<-rbind(table60,table80,table20)
plot(table_new$Income,table_new$Party)
abline(fit1,col="red")
abline(fit2,col="blue")
abline(fit3,col="green")
leg.line<- c("1960","1980","2000")
legend(list(x=3,y=7.3),legend=leg.line,col=c("red","blue","green"),lty=c(1,2,3),merge=TRUE)
```

#Solution 5

* In 1960, Most of the High Income people were in between Independent Democrat and true independent, even low class preferred the same.
* In 2000, Low Income people are either True independent or weak democrat whereas High Income people are Independent democrat or true Independent.

To summarize, People in 2000 are more inclined towards republicans compared to 1960's or earlier. 


#Solution 6
```{r,eval=TRUE,warning=FALSE}
summary(fit1)$coeff
par(mfrow=c(1,2)) 
plot(fit1$residuals,main="Residual Plot of Party and Income 1960")
qqnorm(fit1$residuals,main="Residual QQplot of Party and Income 1960")

```

Slope=0.104 has confidence interval (-0.02,0.23)

We should not take it's meaning literally because:- 

* As seen from Residual Plots there is no linearity between Party and Income. Linear Regression depends on assumptions like Linearity, Homoscedascity, Independence and Normality of errors.

* Linear Regression is not a good fit for categorical data,Both Party and Income are categorical data which should be fit using different model.

#Solution 7
```{r,eval=TRUE,warning=FALSE}
table60<- read.table('C:/Stats/TAKEHOME FINAL/election1960.txt',header=TRUE)
table80<- read.table('C:/Stats/TAKEHOME FINAL/election1980.txt',header=TRUE)
table20<- read.table('C:/Stats/TAKEHOME FINAL/election2000.txt',header=TRUE)
# Party Total in 1960
p160<- sum((table60$Party==1))
p260<- sum((table60$Party==2))
p360<- sum((table60$Party==3))
p460<- sum((table60$Party==4))
p560<- sum((table60$Party==5))
p660<- sum((table60$Party==6))
p760<- sum((table60$Party==7))

# Party Total in 1980

p180<- sum((table80$Party==1))
p280<- sum((table80$Party==2))
p380<- sum((table80$Party==3))
p480<- sum((table80$Party==4))
p580<- sum((table80$Party==5))
p680<- sum((table80$Party==6))
p780<- sum((table80$Party==7))

# Party Total in 2000

p120<- sum((table20$Party==1))
p220<- sum((table20$Party==2))
p320<- sum((table20$Party==3))
p420<- sum((table20$Party==4))
p520<- sum((table20$Party==5))
p620<- sum((table20$Party==6))
p720<- sum((table20$Party==7))

observed<- matrix(c(p160,p260,p360,p460,p560,p660,p760,p180,p280,p380
                    ,p480,p580,p680,p780,p120,p220,p320,p420,p520,p620
                    ,p720),ncol=3,nrow = 7)
colnames(observed)<- c("1960","1980","2000")
rownames(observed)<- c("1","2","3","4","5","6","7")
tt=as.table(observed,header=TRUE)
# Put my results in table
observed=read.table("C:/Stats/Assignment 11/Observed.txt")
observed
p60=sum(observed$X1960)/sum(observed)
p80=sum(observed$X1980)/sum(observed)
p20=sum(observed$X2000)/sum(observed)
p1= sum(observed[1,])
p2= sum(observed[2,])
p3= sum(observed[3,])
p4= sum(observed[4,])
p5= sum(observed[5,])
p6= sum(observed[6,])
p7= sum(observed[7,])
p11= p1*p60
p21= p2*p60
p31= p3*p60
p41= p4*p60
p51= p5*p60
p61= p6*p60
p71= p7*p60
#
p12= p1*p80
p22= p2*p80
p32= p3*p80
p42= p4*p80
p52= p5*p80
p62= p6*p80
p72= p7*p80
#
p13=p1*p20
p23=p2*p20
p33=p3*p20
p43=p4*p20
p53=p5*p20
p63=p6*p20
p73=p7*p20
expected<- matrix(c(p11,p21,p31,p41,p51,p61,p71,p12,p22,p32,p42,p52,p62
                  ,p72,p13,p23,p33,p43,p53,p63,p73),ncol=3,nrow=7)
expected
df=6*2
X2 = sum((observed - expected)^2 / expected)
1 - pchisq(X2, df=df)

```

Since p-value is so low i.e. p-value<0.05, we reject our Null Hypothesis i.e Distribution of Party is independent of year and we conclude that Distribution of Party is dependent on year


#Solution 8

H0:- Population average age is same between 3 years (Null Hypothesis)

H1:- Population average age is not same between 3 years (Alternate Hypothesis)
```{r,eval=TRUE,warning=FALSE}

n1=nrow(table60)
n2=nrow(table80)
n3=nrow(table20)
N=n1+n2+n3
meana=mean(table60$Age)
meanb=mean(table80$Age)
meanc=mean(table20$Age)
grandmean=mean(table_new$Age)
SSB = n1*(meana-grandmean)^2 + n2*(meanb-grandmean)^2 + n3*(meanc-grandmean)^2 
between.df = 2 
between.meansquare = SSB/2
SSW = sum( (table60$Age-meana)^2 ) + sum( (table80$Age-meanb)^2 ) + sum( (table20$Age-meanc)^2 )
within.df = N - 3 
within.meansquare = SSW/within.df
# F-test 
F = between.meansquare/within.meansquare
P=1 - pf(F, df1=between.df, df2=within.df)
P
fit<- lm(table_new$Age~table_new$Year)

# Alternatively to check our solution, we can use ANOVA
anova(fit)

```

p-value=0.003353<0.05 for 95% Confidence Interval hence we reject our Null Hypothesis i.e. Population average age is same for 3 years. We conclude that Population average age differs between 3 years.

#Solution 9

H0:- Population proportion of women remained same in 2000. (Null Hypothesis)

H1:- Population proportion of women were not same in 2000 (Alternate Hypothesis)
```{r,eval=TRUE,warning=FALSE}

female60<- nrow(table60[table60$Sex==2,])
femaleratio60<- female60/nrow(table60)
maleratio60<- 1-femaleratio60

female20<-nrow(table20[table20$Sex==2,])
male20<-nrow(table20[table20$Sex==1,])
observed<- c(female20,male20)
expfem20<- femaleratio60 *nrow(table20)
expmal20<- maleratio60 *nrow(table20)
expected<-c(expfem20,expmal20)

# Pearson's chi-squared
X2 = sum((observed - expected)^2 / expected)
1 - pchisq(X2, df=2-0-1)


# Cross Check values with LR chi-squared test
G2 = 2 * sum(observed * log(observed/expected))
1 - pchisq(G2, df=2-0-1)
```

p-value comes to 0.075 using both Pearson's or Chi-Squared test hence we cannot reject our Null Hypothesis since 0.075 > 0.05 for 95% Confidence Interval

Hence we conclude that Population proportion of women is same in 2000 as it was in 1960.